On modeling for Kerr black holes: Basis learning, QNM frequencies, and spherical-spheroidal mixing coefficients

### 2018-08-07 docs/mvfits_paper/mvf.tex
updating qnm freq section

Second, we will build upon the \gmvp{} approach by considering models of rational functions: polynomials divided by polynomilas.

@@

This latter point is key to the perspective of \gmvp{}: given training data thought to be related to a smooth multivariate function, it may be well approximated by a truncated series expansion in the appropriate coordinate basis.

@@

At this stage, we will also explicitely consider the $j^\mathrm{th}$ samples of the domain, and so refer to $\vec{x}$ as $\vec{x}_j$.

@@

Put another way, rather than two simulteneous greedy optimizations over $R$ and $V-1$ symbols (with $(V-1)R$ iterations), a single greedy process over $V+R$ symbols is performed.

@@

@@

@@

>>>>

Second, we will build upon the \gmvp{} approach by considering models of rational functions: polynomials divided by polynomials.

@@

This latter point is key to the perspective of \gmvp{}: given training data thought to be related to a smooth multivariate function, it may be well approximated by a truncated series expansion in an appropriate coordinate basis.

@@

At this stage, we will also explicitly consider the $j^\mathrm{th}$ samples of the domain, and so refer to $\vec{x}$ as $\vec{x}_j$.

@@

Put another way, rather than two simultaneous greedy optimizations over $R$ and $V-1$ symbols (with $(V-1)R$ iterations), a single greedy process over $V+R$ symbols is performed.

@@

  \label{eq:kappa}

@@

\par Lastly, \fig{fig:qnm_err} shows residual errors.
\par Together, \eqns{eq:cw_fit_1}{eq:cw_fit_9} along with Figures (\ref{fig:qnms})-(\ref{fig:qnm_err}) present precise and accurate fits for the real and imaginary parts of \qnm{} frequencies for gravitational perturbations of Kerr \qnm{s}.

@@

Here we apply \gmvr{} to the spherical-spheroidal mixing coefficients, $\sigma_{\LMlmn}$.
As in the case of the \qnm{} frequencies, we use the domain transformation defined by \eqn{eq:kappa} to simplify the functional form of each $\sigma_{\LMlmn}$.
\par While it is possible to enforce extremal Kerr conditions $\sigma_{\LMlmn}$, we find it effective to first use \gmvr{} to determine a functional form that works for all $\sigma_{\LMlmn}$, and then apply this form to the modeling of all $\sigma_{\LMlmn}$.
% \par \eqns{}
